Forecasting the 2024 U.S. Presidential Election: An Analysis for Battleground States

### 2024-11-01 paper/paper.qmd
Resolved cross referencing issue in the intro.
correct typos and remove whitespace

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-dgplotone
#| 
knitr::include_graphics(here("other", "graphs", "diagnostic_plot_model3.png"))
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-dgplottwo
#| 
knitr::include_graphics(here("other", "graphs", "diagnostic_plot_model6.png"))
```

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-dgplotone

knitr::include_graphics(here("other", "graphs", "diagnostic_plot_model3.png"))
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-dgplottwo

knitr::include_graphics(here("other", "graphs", "diagnostic_plot_model6.png"))
```
